Reverse eigenvalue problem

### 2024-03-08 Docs/NhanesApplExample.Rmd
try NHANES data but truncated to only daytime

set.seed(1114)

@@

I'll take a subset of 500 subject and try different spline basis.

```{r data_split}
# or for sanity checks, use a subset of 1000 subjects
Ntry <- 500
train_id <- sample(unique(df$id), size = Ntry)
train_df <- df %>% filter(id %in% train_id)
```

@@

It seems the flip happened for both cubic spline basis sets, but not the other ones. Also, when sample size gets larger, the flip happens almost certainly for all spline basis.

When I increase the number of PC from 4 to 5, the second and third eigenvalues still flipped almost all the time.

@@

@@

```{r load_est}
load(here("Data/Appl_debias_model.RData"))

>>>>

set.seed(308)

@@

I'll take a subset of 500 subject and try different spline basis. In addition, I truncated the dataset to keep records during the daytime (8am-6pm).

```{r data_split}
# for sanity checks, use a subset of 500 subjects
Ntry <- 500
train_id <- sample(unique(df$id), size = Ntry)
train_df <- df %>% filter(id %in% train_id)

# only the day time? 
# 8am - 6pm (sind: 480 - 1080)
train_df <- train_df %>% filter(sind > 480 & sind <= 1080)
train_df$sind <- train_df$sind-480
J <- max(train_df$sind)
```

@@

It seems for the entire day, the flip happened for both cubic spline basis sets, but not the other ones. Also, when sample size gets larger, the flip happens almost certainly for all spline basis. Bin width did not make a difference. Nor did increasing number of PCs from 4 to 5.

But if I restrict the time period down to 8am-6pm, the eigenvalues are not reversed, and it says that way with larger sample size!

@@

```{r}
df_est_latent %>% 
  filter(id %in% sample(train_id, 4)) %>%
  ggplot()+
  geom_point(aes(x=sind, y=Y), size = 0.5)+
  geom_line(aes(x=sind, y=plogis(eta_hat), col = "Local GLMM"))+
  facet_wrap(~id)
```

@@

```{r load_est}
load(here("Data/Appl_debias_model.RData"))
J <- length(unique(df$sind))
n_bin <- J/bin_w # number of bins
brks <- seq(0, J, by = bin_w) # cutoff points
mid <- (brks+bin_w/2)[1:n_bin] # mid points
